---
title: "Unit 2 Application"
output:
  md_document:
    variant: gfm
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ISLR)
set.seed(1)
```

## We are going to be doing ISLR Question #10 for Chapter 4, but we are going to be updating the dataset.


## Question 1

Load the data "DJ_Weekly.csv" that is in the data folder into R using RStudio's GUI. Make sure the variables are the correct type and the Date is a date.
A. Use glimpse to show that you have loaded the data correctly. Do not print out the full data set.


### Answer

```{r Q1}

```



*************************************

## Question 2

Using mutate, create a new data set that contains the following:
A. Returns. (Hint: Use lag to find the previous periods value. A return is the percentage change from the previous period.)
B. Direction. Use ifelse() to create a variable that is "Up" if the return was positive and "Down" if it was negative.(You may want Direction as a factor.)
C. Lag1. Use lag to add a column with the lagged value of return.
D. Lag2. Use lag(.,2) to add a column with the two period lag.
E. Remove `Adj Close` using select.
F. Remove rows with missing observations using drop_na().
G. Save the resulting data and use head() to print the first few rows.


### Answer

```{r Q2}


```




*************************************



## Question 3

Using data set from Q #2, do the following:

A. Use ggplot to create a scatter plot with Date on the X axis and return on the Y axis.
B. Remove Date and use GGally's ggpairs to create a scatter plot matrix for your data.
C. Do you notice any patterns?


### Answer

```{r Q3}

```




*************************************


## Question 4


Using data set from Q #2, do the following:

A. Use dplyr and summarise to calculate the frequency of "Up" and "Down".
B. Use dplyr with group_by and summarise to find the average return and average volume for "Up" and "Down" weeks.
C. Use dplyr with group_by and summarise to find the standard deviation of return and volume for "Up" and "Down" weeks.
D. Do you notice any patterns?

### Answer

```{r Q4}

```




*************************************


## Question 5

Using data set from Q #2, do the following:
A. Perform a logistic regression with Direction as the response and the two lag variables plus Volume
as predictors.
B. Do any of the predictors appear to be statistically significant? If so,
which ones? (p-values less than .05)
C. Compute the confusion matrix and overall fraction of correct
predictions. Explain what the confusion matrix is telling you
about the types of mistakes made by logistic regression. (Hint: the yardstick package has a confusion matrix function conf_mat(data, truth, estimate))


### Answer

```{r Q5}

```




*************************************



## Question 6

For Questions #6 and #7 you may either use base R, modelR and broom, or tidymodels.

Using data set from Q #2, do the following:

A. Fit the logistic regression model using a training data period
from 1990 to 2018, with Lag2 as the only predictor. (Hint: use as.Date("1jan2000", "%d%b%Y") in a filter)
B. Compute the confusion matrix and the overall fraction of correct predictions
for the held out data (that is, the data from 2019, 2020, and 2021).



### Answer

```{r Q6}

```




*************************************


## Question 7

Repeat question #6 using LDA.


### Answer

```{r Q7}

```




*************************************


## Question 8

Do you feel that QDA or KNN would preform any better for predicting the stock market direction? Why or why not.



### Answer (text only)





*************************************


